Turbulence in compact to giant HII regions

### 2022-08-12 strucfunc_paper.tex
Improve some figure captions

%methods for our analysis
We look for correlations and scaling relations 
between the physical parameters of the \hii{} regions
and the parameters of the fluctuating velocity fields
that we derived in section~\ref{sec:results}.
To accomplish this we implement a hierarchical Bayesian model for linear regression using the \texttt{linmix} Python library, which is based on the procedure of \cite{2007ApJ...665.1489K}.
Thus we fit relations of the form
\(Y = a X + b\)
where \(X = \log_{10} x\) and \(Y = \log_{10} y\)
with \(x, y \in \{d, D, L(\ha), \sigma\pos, r_0, m\}\)
(taken from the physical properties in Table~\ref{tab:regions-properties}
and the derived turbulent parameters of Table~\ref{tab:Res}).
Note that, unlike with an Ordinary Least Squares method,
the \citeauthor{2007ApJ...665.1489K} method
uses an errors-in-variables model that is symmetric in \(X\) and \(Y\).
Thus the fitted relation between the underlying variables
is of the power-law form: \(y = 10^b\, x^a\).
Since the main focus of this paper is the turbulent velocity field,
we restrict consideration to correlations that include
one of the three structure function parameters,
\(\sigma\pos\), \(r_0\), or \(m\), as the  \(y\) variable. 
Additionally, we fit a strictly linear relationship between
the plane-of-sky and line-of-sight velocity dispersions:
\(X = \sigma\pos\), \(Y = \sigma\los\).
The reason for not taking the logarithm in this instance is
both to facilitate comparison with previous studies
and to allow for a zero-point offset in the relation.

@@

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-svsL}
\caption{The log \(\sigma\pos\) - log $L(H_{\alpha})$ plane derived form our results an data in the literature. The markers indicates galactic (triangles), Magellanic (squares) and extragalactic (circles) regions. The black solid line is the input regression line which is described by the equation in the plot, and the red thin lines are a random sample (\num{ \sim 400}) from the posterior distribution within one standard deviation from the slope and the \(Y\)-intercept value. }
\label{fig:sigvsl}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-rvsS}
\caption{
Same information as Fig. \ref{fig:sigvsl} but for the log \(r_0\) - log \(S\) plane derived form our results an data in the literature. 
}
\label{fig:rvsR}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-los-vs-pos}
\caption{
Same information as Fig. \ref{fig:sigvsl} but for the \(\sigma_{\text{pos}}\)-\(\langle \sigma_{\text{los}} \rangle\) plane. The dashed line corresponds to the linear fit obtained by \citet{2011MNRAS.413..705L} which correspond to a sample of small-to-intermediate size \hii{} regions in M33. 
}
\label{fig:los-vs-pos}
\end{figure}

>>>>

%methods for our analysis
We look for correlations and scaling relations 
between the physical parameters of the \hii{} regions
and the parameters of the fluctuating velocity fields
that we derived in section~\ref{sec:results}.
To accomplish this we implement a hierarchical Bayesian model for linear regression using the \texttt{linmix} Python library, which is based on the procedure of \cite{2007ApJ...665.1489K}.
Thus we fit relations of the form
\(Y = a X + b\)
where \(X = \log_{10} x\) and \(Y = \log_{10} y\)
with \(x, y \in \{d, D, L(\ha), \sigma\pos, r_0, m\}\)
(taken from the physical properties in Table~\ref{tab:regions-properties}
and the derived turbulent parameters of Table~\ref{tab:Res}).
Thus the fitted relation between the original variables
is of the power-law form: \(y = 10^b\, x^a\).
Note that, unlike with an Ordinary Least Squares method,
the \citeauthor{2007ApJ...665.1489K} method
uses an errors-in-variables model that allows for
measurement uncertainty in both \(X\) and \(Y\).
Since the main focus of this paper is the turbulent velocity field,
we restrict consideration to correlations that include
one of the three structure function parameters,
\(\sigma\pos\), \(r_0\), or \(m\), as the  \(y\) variable. 
In addition, we fit a strictly linear relationship between
the plane-of-sky and line-of-sight velocity dispersions:
\(X = \sigma\pos\), \(Y = \sigma\los\).
The reason for not taking the logarithm in this instance is
both to facilitate comparison with previous studies
and to allow for a zero-point offset in the relation.

@@

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-svsL}
\caption{
  The relationship between plane-of-sky velocity dispersion,
  \(\log_{10} \sigma\pos\),
  and \hii{} region luminosity,
  \(\log_{10} L(\ha)\),
  derived from our results.
  The markers indicates Galactic (triangles),
  Magellanic (squares) and extragalactic (circles) regions.
  The black solid line is the median linear regression,
  with thin red lines showing 400 random samples from the posterior
  distribution to indicate the uncertainty in the regression.}
\label{fig:sigvsl}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-rvsS}
\caption{
  As Figure~\ref{fig:sigvsl} but for the relationship between
  correlation length of velocity fluctuations,
  \(\log_{10} r_0\),
  and  \hii{} region diameter,
  \(\log_{10} D_{\hii}\).}
\label{fig:rvsR}
\end{figure}

\begin{figure}
\centering 
\includegraphics[width=3in]{Figures/corr-los-vs-pos}
\caption{
  As Figure~\ref{fig:sigvsl} but for the relationship between
  line-of-sight non-thermal velocity dispersion,
  \(\sigma\los\),
  and plane-of-sky velocity dispersion,
  \(\sigma\pos\).
  The dashed line shows the the linear fit obtained by
  \citet{2011MNRAS.413..705L} for a sample of
  small-to-intermediate size \hii{} regions in the M33 galaxy. 
}
\label{fig:los-vs-pos}
\end{figure}
